Symbolic Weighted Language Models and\\ Parsing over Infinite Alphabets

### 2021-06-10 introduction.tex
revise section parsing

The main contributions of the paper are: 
($i$)~the introduction of automata, \SWA, transducers, \SWT (Section~\ref{section:SWA}),
and visibly pushdown automata \SWVPA (Section~\ref{sec:SWVPA}),
generalizing the corresponding classes of symbolic and weighted models, 
%for the weighted computation on (nested) words over infinite alphabets;  
($ii$)~a polynomial best-search algorithm for \SWVPA, %(Section~\ref{sec:best})
% a framework for parsing over infinite alphabets, 
and ($iii$)~a uniform framework (Section~\ref{sec:parsing}) for parsing over infinite alphabets, 
the keys to which are 
($iii.a$)~the \SWT-based definition of generic edit distances between input and output (yield) words,
and ($iii.b$)~the use in this context of nested words, and \SWVPA, 
instead of syntax trees and grammars. %(\S~\ref{sec:trees}).
%
%Finally, Section~\ref{sec:transcription} describes
%the implemented application %of this approach 
%to automated music transcription
%that motivated this study.

>>>>

The main contributions of the paper are: 
($i$)~the introduction of automata, \SWA, transducers, \SWT (Section~\ref{section:SWA}),
and visibly pushdown automata \SWVPA (Section~\ref{sec:SWVPA}),
generalizing the corresponding classes of symbolic and weighted models, 
%for the weighted computation on (nested) words over infinite alphabets;  
($ii$)~a polynomial best-search algorithm for \SWVPA, %(Section~\ref{sec:best})
% a framework for parsing over infinite alphabets, 
and ($iii$)~a uniform framework (Section~\ref{sec:parsing}) for parsing over infinite alphabets, 
the keys to which are 
($iii.a$)~the \SWT-based definition of generic edit distances between input and output (yield) words,
and ($iii.b$)~the use, convenient in this context, 
of nested words, and \SWVPA, 
instead of syntax trees and grammars. %(\S~\ref{sec:trees}).
%
%Finally, Section~\ref{sec:transcription} describes
%the implemented application %of this approach 
%to automated music transcription
%that motivated this study.
